hormones

### 2019-10-09 analysis/07_hormones.Rmd
new hormone figs

a <- ggplot(characterization, aes(x = treatment, y = `Prolactin ng/mL`, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(subtitle = "Observed prolactin",
       y = "Concentration (ng/mL)", x = NULL) +
  #geom_text(data = df, aes(x,y, label = text), color = "darkgrey") +
      ylim(0,120)

@@

e <- manipulation %>%
  ggplot( aes(x = treatment, y = `Prolactin ng/mL`)) +
    geom_boxplot(aes(fill = sex, alpha = 0.5)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom",
          legend.title = element_blank()) +
    ylim(0,125) +
    labs(subtitle = "Manipulation",
       y = NULL, x = NULL) + 
  scale_alpha(guide = 'none')

plot_grid(a,b,e, nrow = 1, rel_widths = c(1.1,.75,.8))

>>>>

a <- ggplot(characterization, aes(x = treatment, y = `Prolactin ng/mL`, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(subtitle = "Characterization", y = "Prolactin (ng/mL)", x = NULL) +
  #geom_text(data = df, aes(x,y, label = text), color = "darkgrey") +
      ylim(0,120) 
a

@@

e <- manipulation %>%
  ggplot( aes(x = treatment, y = `Prolactin ng/mL`)) +
    geom_boxplot(aes(fill = sex)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom",
          legend.title = element_blank()) +
    ylim(0,125) +
    labs(subtitle = "Manipulation",
       y = "Prolactin (ng/mL)", x = NULL)
e

plot_grid(a,e, nrow = 1)
